Trans-Dimensional Bayesian Inference for Gravitational Lens Substructures

### 2015-09-07 Papers/ms.tex
marginal likelihood and information

{\revisions
As with the easy dataset, the standardised residuals of the sampled models
resembled noise.
}

>>>>

{\revisions
The estimated marginal likelihood of our model, for the `harder' simulated data,
is
$\ln\left[p(\boldsymbol{D} | \boldsymbol{\theta})\right] \approx -5671.9$, and
the information (Kullback-Leibler divergence from the prior to the posterior)
is $\mathcal{H} \approx 155.7$ nats. 
As with the easy dataset, the standardised residuals of the sampled models
resembled noise.
}
